\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[left=2cm, right=2cm, top=2cm]{geometry}
\usepackage[utf8]{inputenc}
\begin{document}
\textbf{\huge\centerline{Ram Mahesh}}
\line(1,0){500}
\\
Room No 313,\hfill Contact: +919770018168\\
Aryabhatt Hostel,\hfill e-mailID: ram01189@gmail.com\\
Institute of Engineering and Technology,
Lucknow\\
Uttar Pradesh -226021
\section*{Objective}
To pursue career in Electronics where I could use my skills for the development of advanced
technology for the benefit of mankind.
\section*{Education}
\begin{table}[!h]
  \begin{center}
    \begin{tabular}{|p{4cm}|p{5cm}|p{4cm}|p{2cm}|p{2cm}|}
 \hline
  \textbf{Degree} & \textbf{College/School} & \textbf{University}&        \textbf{Passing Year}& \textbf{Passing Percentage}\\
 \hline
      B.Tech \\Electronics \& Communication Engineering & Institute of Engineering \&  Technology,Lucknow       
      & Abdul Kalam Technical University,Uttar Pradesh & 2020\\
  \hline
      SSC & New Green Field Public Academy ,Indore(M.P.) & CBSE & 2015& 86.60\\
      \hline
 HSC & Lucknow Public School ,Rae Bareli & CBSE &2013 & 10.0\\
\hline
\end{tabular}
  \end{center}
\end{table}


\section*{Projects}
\begin{enumerate}
  \item{\textbf{Home Automation System}} :\\(a) Using a DTMF, ARDUINO and Relay I made a system
which allows user to control the\ Home appliances by making a Call on the Mobile
Phone attached to system\\
(b) Using Android App developed from MIT App Inventor
and Bluetooth which enables user to control the Home appliances using smartphone
\item {\textbf{A website on Parmarth:}}\\ Using HTML-5, CSS-3, PHP worked on the front end developement of the website of social club.
Parmarth a social club of institute.
\item {\textbf{Power Supply Box:}}\\ Using the diodes and transformer made a power supply box that converted 220V AC to regulated 9V DC power supply.
\item {\textbf{IOT Basic Project}}\\ Using the Raspberry Pi-3 transferred the values of Temperature and Humidity sensor (DHT11) to the www.thingsspeak.com. 
\item {\textbf{Transporter Bot(E-YRC)}}\\ Using the Firebird-V and the ZigBee communication and Blender animation, we designed  a bot capable of transporting the crated to Truck from field.    
\end{enumerate}

\section*{Training\& Internship}
\begin{enumerate}
  \item Building Arduino Robots and Devices by MIPT \href{https://drive.google.com/open?id=1OdgRvGUVJlKDj6jBgbTeKgBTcAWb4hAs}{Certificate}. 
\item Programming for Everybody (Introductory course on Python) by University of Michigan
\href{https://drive.google.com/open?id=1bFMwfXUaMAlEdo0C462mUvpyfJMTv2jr}{Certificate}.
\item An Introduction to Programming the Internet of things by University of California Irvine \href{https://drive.google.com/open?id=1Cly1gg0PYxZJb4zLB8IZnftkQj3MmyOu}{Certificate}.
\item An Introduction to Python for Data Science \href{https://drive.google.com/open?id=1yZQDmsZnb0BlFxZFdd0phYQZYy7ax6FA}{Certificate}.
\item Database Design with My-SQL\href{https://drive.google.com/open?id=1Oa-SXJebTJWY2u02TiFzb9QqZ7XdkYcO}{Certificate}.
\end{enumerate}


\section*{Technical Skills}
\begin{enumerate}
  \item Has basic knowledge of Linux OS \& Terminal.
  \item Has a good hand on experience of electronics circuits.
  \item Has a knowledge of the Raspberry PI-3 \& Microcontrollers   Arduino, MSP430
  \item Participated in the AIRC(Line Follower \& Wall Follower event) at Techkriti annual technical fest of IITKanpur 
  \item Zonal Round Winner in the IARC (All India Research Competetion 2018) at Techkriti annual technical fest of IITKanpur
  \item \textbf{Programming Language}: - C, Python, Embedded C*
  \item \textbf{ Web Development:-} HTML-5, CSS-3, PHP*
  \item\textbf{Development Software:-} MATLAB,Arduino,P-Spice,OrCad,Linux(Rasbpian),OpenCV*.
\end{enumerate}

\section*{Soft Skills}
\begin{enumerate}
  \item Hardworking
  \item Passionate for Robotics \& Electronics
  \item Endeavour to learn new skills.
  \item Responsible
  \end{enumerate}
  
\section*{Extra-Curricular Activities}
\begin{enumerate}
\item Attended a 7 Day Faculty Developement Programme on Human Values \& Professional Ethics organised By
AKTU, Uttar Pradesh
\item Attended a 7 Day session on Inner Engineering by ISHA Foundation.
\item Assistant Coordinator in Abhigyaan (University Technical Fest)
\item Assistant Coordinator in PARAKRAM (College Technical Fest)
\item Mess Committee member of Aryabhatt Hostel.
\end{enumerate}



\section*{Personal Details}
{\large {Father's Name:- \hspace{1.1cm} Shiv Raj Yadav\\
Mother's Name:- \hspace{1cm} Lt. Chandra Vati\\
Gender:-\hspace{2.9cm}Male\\
Nationality:-\hspace{2.0cm}Indian\\
Marital Status:-\hspace{1.4cm}Single\\
}}
\section*{\large {Reference}}
Dr. Subodh Wairya\\
Professor \& Head of Department\\
Electronics Engineering Department\\
Institute of Engineering \& Technology (I.E.T), Lucknow\\
An Autonomous Constitute Institute of Dr. A. P. J. Abdul Kalam Technical University, Lucknow, India)
Lucknow-226021, U.P, India
+91 9044039593\\
\href{subodh.wariya@ietlucknow.ac.in}{subodh.wariya@ietlucknow.ac.in}
\section*{\large {Declaration}}
All the information mentioned in the resume are correct to the best of my knowledge and believe.
\section*{\large {Date}}
18 April 2018
 
\end{document}
